Nearest Neighbour Methods for Length of Stay Prediction

### 2015-02-16 papers/paper.tex
Add graphs for no-threshold feature selectors with reduced classifier set

\subsection{Statistical Significance}

\subsection{Experimental Setup and Procedure}
The steps that we took to evaluate the performance of the various classifiers
and feature selection methods were:
\begin{enumerate}
\item For both the discretised and non-discretised data set, we trained all 7
classifiers without feature selection. Evaluation was performed using ten runs
of \textit{ten-fold stratified cross-validation}.
\item Then, for each data set, we evaluated the effect of the 3 automatic
feature
selection methods on each of the 7 classifiers listed above, giving us 21
configurations for the discretised and non-discretised data set.
\item In order to ensure that the baseline in the literature was comparable
to our work, we used the baseline features and applied their method, logistic
regression, to obtain a measure of performance on the non-discretised data set.
We also evaluated this feature set against the rest of the 6 classifiers, and
repeated this using the discretised data.
\item Additionally, the expert-selected features were tested against all 7
classifiers, with both the discretised and non-discretised data.
\end{enumerate}

@@

\begin{figure*}[htbp]
\begin{subfigure}{.48\textwidth}
\includegraphics[width=\textwidth]{../thesis/images/results/tr-nofs-acc.eps}
\caption{}
\label{}
\end{subfigure}%
\begin{subfigure}{.55\textwidth}
\includegraphics[width=\textwidth]{../thesis/images/results/tr-nofs-auc.eps}
\caption{}
\label{}
\end{subfigure}

\begin{subfigure}{.48\textwidth}
\includegraphics[width=\textwidth]{../thesis/images/results/tr-dinh-acc.eps}
\caption{}
\label{}
\end{subfigure}%
\begin{subfigure}{.55\textwidth}
\includegraphics[width=\textwidth]{../thesis/images/results/tr-dinh-auc.eps}
\caption{}
\label{}
\end{subfigure}

\begin{subfigure}{.48\textwidth}
\includegraphics[width=\textwidth]{../thesis/images/results/tr-expert-acc.eps}
\caption{}
\label{}
\end{subfigure}%
\begin{subfigure}{.55\textwidth}
\includegraphics[width=\textwidth]{../thesis/images/results/tr-expert-auc.eps}
\caption{}
\label{}
\end{subfigure}

\begin{subfigure}{.48\textwidth}
\includegraphics[width=\textwidth]{../thesis/images/results/tr-wrapper-acc.eps}
\caption{}
\label{}
\end{subfigure}%
\begin{subfigure}{.55\textwidth}
\includegraphics[width=\textwidth]{../thesis/images/results/tr-wrapper-auc.eps}
\caption{}
\label{}
\end{subfigure}
\caption[]{Comparison of accuracy and AUC between classifiers for each non-threshold feature selection method, grouped by whether or not discretisation was applied.}
\label{}
\end{figure*}

>>>>

\subsection{Experimental Setup and Procedure}
The steps that we took to evaluate the performance of the various classifiers
and feature selection methods were:
\begin{enumerate}
\item For both the discretised and non-discretised data set, we trained all 7
classifiers without feature selection. Evaluation was performed using ten runs
of \textit{ten-fold stratified cross-validation}.
\item Then, for each data set, we evaluated the effect of the 3 automatic
feature
selection methods on each of the 7 classifiers listed above, giving us 21
configurations for the discretised and non-discretised data set.
\item In order to ensure that the baseline in the literature was comparable
to our work, we used the baseline features and applied their method, logistic
regression, to obtain a measure of performance on the non-discretised data set.
We also evaluated this feature set against the rest of the 6 classifiers, and
repeated this using the discretised data.
\item Additionally, the expert-selected features were tested against all 7
classifiers, with both the discretised and non-discretised data.
\item Paired $t$-tests for statistical significance were carried out to
determine whether or not discrepancies in performance were significant.
\end{enumerate}

@@

\begin{figure*}[htbp]
\begin{subfigure}{.48\textwidth}
\includegraphics[width=\textwidth]{results/tr-nofs-acc.eps}
\caption{}
\label{}
\end{subfigure}%
\begin{subfigure}{.55\textwidth}
\includegraphics[width=\textwidth]{results/tr-nofs-auc.eps}
\caption{}
\label{}
\end{subfigure}

\begin{subfigure}{.48\textwidth}
\includegraphics[width=\textwidth]{results/tr-dinh-acc.eps}
\caption{}
\label{}
\end{subfigure}%
\begin{subfigure}{.55\textwidth}
\includegraphics[width=\textwidth]{results/tr-dinh-auc.eps}
\caption{}
\label{}
\end{subfigure}

\begin{subfigure}{.48\textwidth}
\includegraphics[width=\textwidth]{results/tr-expert-acc.eps}
\caption{}
\label{}
\end{subfigure}%
\begin{subfigure}{.55\textwidth}
\includegraphics[width=\textwidth]{results/tr-expert-auc.eps}
\caption{}
\label{}
\end{subfigure}

\begin{subfigure}{.48\textwidth}
\includegraphics[width=\textwidth]{results/tr-wrapper-acc.eps}
\caption{}
\label{}
\end{subfigure}%
\begin{subfigure}{.55\textwidth}
\includegraphics[width=\textwidth]{results/tr-wrapper-auc.eps}
\caption{}
\label{}
\end{subfigure}
\caption[]{Comparison of accuracy and AUC between classifiers for each non-threshold feature selection method, grouped by whether or not discretisation was applied.}
\label{}
\end{figure*}
